An eight-year-long low-frequency earthquake catalog for Southern Cascadia

### 2022-02-03 paper/supplement.tex
Work on revisions
Ready to submit

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_FAME.eps}
\caption{Same as Figure 3 from the main text, but without filtering the LFEs. They are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
\label{pngfiguresample}
\end{figure}

@@

\begin{table}[hbt!]
\caption{Thresholds used to clean the catalogs. An LFE is kept in the catalog if its cross-correlation value multiplied by the number of channels recording when it was detected is higher than the threshold. The threshold is missing for the families for which there were not enough permanent stations with good templates to obtain reliable LFE detections.}
\centering
\scriptsize
\begin{tabular}{c c c}
\hline
Family & Threshold 2007-2009 & Threshold 2004-2011 \\
\hline
080401.05.050 & 1.4 & 1.9 \\
080405.11.042 & 2.0 & 1.6 \\
080408.08.007 & 1.7 & 1.5 \\
080408.15.023 & 2.0 & 1.3 \\
080408.08.029 & 2.3 & 1.4 \\
080408.16.026 & 1.8 & 1.4 \\
080410.01.050 & 3.5 & 1.3 \\
080410.09.032 & 3.9 & 1.4 \\
080410.12.039 & 1.9 & 1.3 \\
080410.12.040 & 5.4 & 2.3 \\
080411.04.013 & 3.4 & 1.5 \\
080411.04.023 & 3.6 & 1.5 \\
080410.13.055 & 1.9 & 1.3 \\
080412.03.029 & 2.2 & 1.0 \\
080412.11.038 & 2.2 & 1.3 \\
080412.22.047 & 3.2 & 1.5 \\
080413.13.026 & 2.2 & 1.3 \\
080412.22.040 & 3.5 & 1.6 \\
080413.07.015 & 2.0 & 1.6 \\
080413.07.023 & 1.8 & 1.4 \\
080413.16.058 & 2.2 & 0.1 \\
080413.18.013 & 2.6 & 1.2 \\
080413.20.036 & 2.1 & 1.1 \\
080414.12.016 & 2.0 & 1.2 \\
080414.12.020 & 1.5 & 1.2 \\
080414.10.058 & 1.8 & 1.2 \\
080414.18.003 & NA & NA \\
080415.11.006 & 4.6 & 1.6 \\
080415.11.008 & 3.0 & 1.8 \\
080415.24.028 & 2.5 & 1.7 \\
080416.15.003 & 2.8 & 1.7 \\
080418.03.001 & 5.0 & 1.5 \\
080415.19.030 & 2.9 & 1.9 \\
080419.24.054 & 3.4 & 2.2 \\
080416.13.033 & 3.9 & 2.0 \\
080417.15.043 & 3.3 & 1.7 \\
080418.02.049 & 3.7 & 1.6 \\
080419.04.046 & 3.5 & 1.5 \\
080420.01.019 & 2.3 & 1.6 \\
080420.04.009 & 2.2 & 1.4 \\
080420.05.032 & 3.0 & 1.8 \\
080420.08.042 & 1.8 & 1.5 \\
080421.14.048 & 2.1 & 1.6 \\
080421.15.050 & 1.9 & 1.5 \\
080421.16.053 & 3.0 & 1.4 \\
080421.16.054 & 2.3 & 1.4 \\
080421.17.056 & 2.1 & 1.3 \\
080421.23.033 & 2.7 & 1.4 \\
080422.13.003 & 3.2 & 1.7 \\
080422.12.039 & 1.7 & 1.1 \\
080422.13.043 & 2.7 & 1.6 \\
080422.15.030 & 2.0 & 1.5 \\
080424.04.058 & 3.3 & 1.8 \\
080424.05.060 & 2.2 & 1.7 \\
080426.05.008 & 1.8 & 1.6 \\
080426.06.027 & 2.1 & 1.8 \\
080426.20.030 & 1.5 & 1.7 \\
080427.04.052 & 2.5 & 1.5 \\
080427.13.036 & 2.1 & 1.5 \\
080427.20.043 & 2.5 & 2.0 \\
080429.15.005 & NA & NA \\
080326.07.004 & NA & NA \\
080326.07.048 & NA & NA \\
080326.08.015 & 2.7 & 1.0 \\
080326.09.007 & NA & NA \\
080328.09.029 & NA & NA \\
\hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[hbt!]
\noindent\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm},clip]{figures/unfiltered_FAME.eps}
\caption{Same as Figure 3 from the main text, but without filtering the LFEs. There are many false detections at the beginning and the end of the catalog because the FAME stations were not yet installed / already removed.}
\label{pngfiguresample}
\end{figure}

@@

\begin{table}[hbt!]
\caption{Thresholds used to clean the catalogs. An LFE is kept in the catalog if its cross-correlation value multiplied by the number of channels recording when it was detected is higher than the threshold. The threshold is missing for the families for which there were not enough permanent stations with good templates to obtain reliable LFE detections.}
\centering
\scriptsize
\begin{tabular}{c c c}
\hline
Family & Threshold 2007-2009 FAME catalog & Threshold 2007-2009 networks catalog\\
\hline
080401.05.050 & 1.4 & 1.9 \\
080405.11.042 & 2.0 & 1.6 \\
080408.08.007 & 1.7 & 1.5 \\
080408.15.023 & 2.0 & 1.3 \\
080408.08.029 & 2.3 & 1.4 \\
080408.16.026 & 1.8 & 1.4 \\
080410.01.050 & 3.5 & 1.3 \\
080410.09.032 & 3.9 & 1.4 \\
080410.12.039 & 1.9 & 1.3 \\
080410.12.040 & 5.4 & 2.3 \\
080411.04.013 & 3.4 & 1.5 \\
080411.04.023 & 3.6 & 1.5 \\
080410.13.055 & 1.9 & 1.3 \\
080412.03.029 & 2.2 & 1.0 \\
080412.11.038 & 2.2 & 1.3 \\
080412.22.047 & 3.2 & 1.5 \\
080413.13.026 & 2.2 & 1.3 \\
080412.22.040 & 3.5 & 1.6 \\
080413.07.015 & 2.0 & 1.6 \\
080413.07.023 & 1.8 & 1.4 \\
080413.16.058 & 2.2 & 0.1 \\
080413.18.013 & 2.6 & 1.2 \\
080413.20.036 & 2.1 & 1.1 \\
080414.12.016 & 2.0 & 1.2 \\
080414.12.020 & 1.5 & 1.2 \\
080414.10.058 & 1.8 & 1.2 \\
080414.18.003 & NA & NA \\
080415.11.006 & 4.6 & 1.6 \\
080415.11.008 & 3.0 & 1.8 \\
080415.24.028 & 2.5 & 1.7 \\
080416.15.003 & 2.8 & 1.7 \\
080418.03.001 & 5.0 & 1.5 \\
080415.19.030 & 2.9 & 1.9 \\
080419.24.054 & 3.4 & 2.2 \\
080416.13.033 & 3.9 & 2.0 \\
080417.15.043 & 3.3 & 1.7 \\
080418.02.049 & 3.7 & 1.6 \\
080419.04.046 & 3.5 & 1.5 \\
080420.01.019 & 2.3 & 1.6 \\
080420.04.009 & 2.2 & 1.4 \\
080420.05.032 & 3.0 & 1.8 \\
080420.08.042 & 1.8 & 1.5 \\
080421.14.048 & 2.1 & 1.6 \\
080421.15.050 & 1.9 & 1.5 \\
080421.16.053 & 3.0 & 1.4 \\
080421.16.054 & 2.3 & 1.4 \\
080421.17.056 & 2.1 & 1.3 \\
080421.23.033 & 2.7 & 1.4 \\
080422.13.003 & 3.2 & 1.7 \\
080422.12.039 & 1.7 & 1.1 \\
080422.13.043 & 2.7 & 1.6 \\
080422.15.030 & 2.0 & 1.5 \\
080424.04.058 & 3.3 & 1.8 \\
080424.05.060 & 2.2 & 1.7 \\
080426.05.008 & 1.8 & 1.6 \\
080426.06.027 & 2.1 & 1.8 \\
080426.20.030 & 1.5 & 1.7 \\
080427.04.052 & 2.5 & 1.5 \\
080427.13.036 & 2.1 & 1.5 \\
080427.20.043 & 2.5 & 2.0 \\
080429.15.005 & NA & NA \\
080326.07.004 & NA & NA \\
080326.07.048 & NA & NA \\
080326.08.015 & 2.7 & 1.0 \\
080326.09.007 & NA & NA \\
080328.09.029 & NA & NA \\
\hline
\end{tabular}
\end{table}
